---
title: "R Notebook"
output: rmarkdown::github_document
---

# ANPR-Based Automatic Abnormal Traffic Flow Detection
The following page is made for anpr flow data exploration purpose. The data is taken from github repo <https://github.com/ppintosilva/congestion18tynewear/blob/master/data-raw/events.R>. We'll set-up caching for this notebook given how computationally expensive some of the code we will write can get.
```{r setup}
knitr::opts_chunk$set(cache=TRUE)
options(scipen=9999)
rm(list=ls())
```

## Importing libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(sf)
library(maotai)
library(ggpubr)
```

## Define corridor level
```{r}
corridor_levels = c(1, 2, 3)
```

## Create flow dataframe for 2-3 camera pairs
```{r}
flows <- read_csv(
  file = "data/corridor_A184_WEST_3cameras.csv",
  col_names = TRUE,
  col_types = list(
    o = col_integer(),
    d = col_integer(),
    t = col_datetime(),
    flow = col_integer(),
    mean_speed = col_double()
  )
) %>%
  mutate(o = factor(o, levels = corridor_levels),
         d = factor(d, levels = corridor_levels))
```

## Get the flow data on weekday across 2-3 pair
```{r}
flows_23_weekday <- 
  flows %>%
  filter(o == 2 & d == 3) %>%
  filter(wday(t, week_start = 1) < 6)
```

## Daily flow for corridor 2-3
```{r}
p_daily_flow <-
  flows_23_weekday %>%
  ggplot() +
  geom_line(
    aes(x = hms::as_hms(t), y = flow, group = as_date(t)),
    alpha = .5
  ) + 
  scale_x_time(
    name = "Time",
    breaks = hms::hms(hours = seq(2, 22, 4)),
    labels = scales::label_time("%Hh")
  ) + 
  theme_bw()
p_daily_flow
```

## Flow Descriptive Stats
```{r}
flows_23_weekday %>%
  group_by(as_date(t)) %>%
  summary()
```


```{r}
p_daily_mean_speed <-
  flows_23_weekday %>%
  ggplot() +
  geom_line(
    aes(x = hms::as_hms(t), y = mean_speed, group = as_date(t)),
    alpha = .5
  ) + 
  scale_x_time(
    name = "Time",
    breaks = hms::hms(hours = seq(2, 22, 4)),
    labels = scales::label_time("%Hh")
  ) + 
  theme_classic()
p_daily_mean_speed
sum(is.na(flows_23_weekday$mean_speed))
sum(is.na(flows_23_weekday$flow))
```



### Classify daily flow based on threshold
```{r}
expected_flow <-
  flows_23_weekday %>%
  mutate(time = hms::as_hms(t)) %>%
  group_by(o,d,time) %>%
  summarise(
    median_flow = median(flow)
  )
```

```{r}
deviation_flow <-
  flows_23_weekday %>%
  mutate(time = hms::as_hms(t)) %>%
  group_by(o, d, time) %>%
  summarise(
    mad_flow = mad(flow)
  )
```

```{r}
flow_with_expected <- 
  flows_23_weekday %>%
  mutate(time = hms::as_hms(t)) %>%
  inner_join(expected_flow, by = c("o", "d", "time"))
```

```{r}
flow_with_expected <- 
  flow_with_expected %>%
  mutate(har_mean_speed = mean_speed - (var(mean_speed, na.rm = TRUE)/mean_speed))
```

```{r}
cor.test(flow_with_expected$flow, flow_with_expected$har_mean_speed, method = "pearson")
```

```{r}
cor.test(flow_with_expected$flow, flow_with_expected$mean_speed, method = "pearson")
```

```{r}
p_median <- ggplot(flow_with_expected) + 
  geom_line(aes(x = time, y = flow, group = date(t)), color = "grey") +
  geom_line(aes(x = time, y = median_flow), color = "black") +
  scale_x_time(
    name = "Time",
    breaks = hms::hms(hours = seq(2, 24, 4)),
    labels = scales::label_time("%H:%M")
  ) +
  theme_bw()
p_median
```

```{r}
flow_with_expected %>%
  filter(as_date(t) == "2018-10-02") %>%
  mutate(flow_diff = abs(flow - median_flow)) %>%
  mutate(outlier = ifelse(flow_diff > 40, TRUE, FALSE)) %>%
  ggplot() +
  geom_line(aes(x = time, y = flow_diff)) +
  geom_hline(yintercept = 40, color = "red") +
  theme_bw()
```

## Clustering flow data using EP-MEANS
```{r}
p_daily_ecdf <-
  flow_with_expected %>%
  ggplot() +
  stat_ecdf(
    aes(x = flow, group = as_date(t)),
    alpha = .7
  ) +
  xlab("Vehicle count per time period (15min)") +
  ylab("Cumulative probability") +
  theme_bw()
p_daily_ecdf
```

## EP Means
### Create flows_ecd23 (give index based on date and o-d pair) 
```{r}
flows_ecd23 <-
  flow_with_expected %>%
  mutate(dayt = as_date(t)) %>%
  group_by(o, d, dayt) %>%
  summarise(ecd = list(ecdf(flow))) %>%
  group_by(dayt) %>%
  mutate(date_index = group_indices()) %>%
  group_by(o, d) %>%
  mutate(group_id = group_indices())
head(flows_ecd23)
```
```{r}
flow_with_expected %>%
  filter(as_date(t) == c("2018-04-02", "2018-01-01"))
```

```{r}
p_01_ecdf <-
  flow_with_expected %>%
  filter(as_date(t) == c("2018-04-02", "2018-01-02")) %>%
  ggplot() +
  stat_ecdf(
    aes(x = flow, group = as_date(t)),
    alpha = .7
  ) +
  theme_bw() +
  xlab("Vehicle count per time period (15min)") +
  ylab("Cumulative probability") 
p_01_ecdf
```

### Apply EP Means to flows_ecd23 with number of cluster == 2
```{r}
epout_k2 <- flows_ecd23 %>%
  group_map(~ { maotai::epmeans(.x$ecd, k = 2) })
epout_k2
```

### Create daily cluster dataframe
```{r}
daily_cluster_ids <- epout_k2 %>%
  lapply(function(x) x$cluster %>%
           enframe(name = "date_index", value = "cluster")) %>%
  enframe(name = "group_id", value = "value") %>%
  unnest(value)
head(daily_cluster_ids)
```

### Calculate 80% quantile in flow data 
```{r}
flow_80quantiles <- flows_23_weekday %>%
  group_by(o,d) %>%
  summarise(quantile80 = quantile(flow, 0.8))
```

### Create centroids
Assume that the centroids which corresponds to "typical" traffic is the one who carries more traffic most of the times, i.e. will have lower cummulative probability of carrying less or equal than 80th percentile of the flow
```{r}
ecd_centroids_k2 <- epout_k2 %>%
  lapply(function(x) x$centers %>% enframe(name = "cluster", value = "centroid")) %>%
  enframe(name = "group_id", value = "value") %>%
  unnest(value) %>%
  inner_join(flows_ecd23 %>% distinct(o,d) %>% mutate(group_id = group_indices()), 
             by = "group_id") %>%
  select(-group_id) %>%
  select(o, d, cluster, centroid) %>%
  # label which centroid is typical and atypical
  # for a high quantile (e.g. 80% quantile)
  inner_join(flow_80quantiles, by = c("o", "d")) %>%
  group_by(o, d, cluster) %>%
  mutate(prob80 = centroid[[1]](quantile80)) %>%
  group_by(o, d) %>%
  arrange(prob80) %>%
  mutate(cluster_label = c("typical", "atypical")) %>%
  mutate(cluster_label = factor(cluster_label)) %>%
  arrange(o, d, prob80)
```

```{r}
max_flow <- max(flows$flow)
npoints = 500
```

```{r}
ecd_centroids_k2_xy <- 
  ecd_centroids_k2 %>%
  group_by(o, d, cluster) %>%
  group_modify(~{
    tibble(
      cluster_label = .$cluster_label,
      ecd_x = seq(0, max_flow, length.out = npoints)
      ) %>%
        mutate(ecd_y = .x$centroid[[1]](ecd_x))
  })
```

```{r}
od_day_labels <- flows_ecd23 %>%
  inner_join(daily_cluster_ids, by = c("group_id", "date_index")) %>%
  select(-c(date_index, group_id, ecd)) %>% 
  inner_join(
    ecd_centroids_k2 %>% distinct(o, d, cluster, cluster_label),
    by = c("o", "d", "cluster")
  )
```

```{r}
flows_23_labelled <- 
  flows_23_weekday %>% 
  mutate(dayt = as_date(t)) %>%
  mutate(month = month(t)) %>%
  inner_join(od_day_labels %>% select (-cluster), by = c("o", "d", "dayt"))
```

```{r}
flows_23_labelled[flows_23_labelled$month == 5,]
```

```{r}
p_all_clustered_ecdf <-
  flows_23_labelled %>%
  mutate(tday = factor(as_date(t))) %>%
  ggplot() +
  stat_ecdf(
    aes(x = flow, group = tday, colour = cluster_label),
    alpha = .6
  ) + 
  geom_line(
    data = ecd_centroids_k2_xy,
    mapping = aes(x = ecd_x, y = ecd_y, colour = cluster_label),
    size = 2
  ) + 
  geom_vline(
    xintercept = ecd_centroids_k2$quantile80, 
    linetype = "dotted", 
    size = 1.0
    ) +
  geom_hline(
    yintercept = ecd_centroids_k2$prob80,
    linetype = "dashed",
    size = 1.0
  ) +
  scale_color_grey(name = "Daily behaviour") + 
  theme_bw() +
  xlab("Vehicle count per time period (15min)") +
  ylab("Cumulative probability")
p_all_clustered_ecdf
```

```{r}
p_test <- 
  flows_23_labelled %>%
  mutate(tday = factor(as_date(t))) %>%
  ggplot() +
  stat_ecdf(
    aes(x = flow, group = tday, colour = cluster_label),
    alpha = .6
  ) + 
  geom_line(
    data = ecd_centroids_k2_xy,
    mapping = aes(x = ecd_x, y = ecd_y, colour = cluster_label),
    size = 2
  )
p_test
```


```{r}
p_daily_flow_labelled <- 
  flows_23_labelled %>%
  ggplot() +
  geom_line(
    aes(x = hms::as_hms(t), y = flow, group = as_date(t)), alpha = .5
  ) + 
  scale_x_time(
    name = "Time",
    breaks = hms::hms(hours = seq(2,22,4)),
    labels = scales::label_time("%Hh")
  ) + 
  facet_wrap(~cluster_label) +
  theme_bw()
p_daily_flow_labelled
```

```{r}
p_daily_speed_labelled <- 
  flows_23_labelled %>%
  ggplot() +
  geom_line(
    aes(x = hms::as_hms(t), y = mean_speed, group = as_date(t)), alpha = .5
  ) + 
  scale_x_time(
    name = "Time",
    breaks = hms::hms(hours = seq(2,22,4)),
    labels = scales::label_time("%Hh")
  ) + 
  facet_wrap(~cluster_label) +
  theme_bw()
p_daily_speed_labelled
```

### Check correlation between labelled flow vs speed
```{r}
x <- flows_23_labelled %>% filter(flow, cluster_label == "typical")
y <- flows_23_labelled %>% filter(mean_speed, cluster_label == "typical")
a <- flows_23_labelled %>% filter(flow, cluster_label == "atypical")
b <- flows_23_labelled %>% filter(mean_speed, cluster_label == "atypical")

cor.test(x$flow, y$mean_speed, method = "pearson")
cor.test(a$flow, b$mean_speed, method = "pearson")
```

## Estimate function for each classes
```{r}
flows_23_atypical <- flows_23_labelled[flows_23_labelled$cluster_label == 'atypical',]
flows_23_typical <- flows_23_labelled[flows_23_labelled$cluster_label == 'typical',]
```

### Mean for atypical phenomenon in road segment 2-3
```{r}
flows_23_atypical$time <- hms::as_hms(flows_23_atypical$t)
flows_23_atypical_mean <- aggregate(flows_23_atypical[,4], list(as.character(flows_23_atypical$time)), mean)
```

### Mean for typical phenomenon in road segment 2-3
```{r}
flows_23_typical$time <- hms::as_hms(flows_23_typical$t)
flows_23_typical_mean <- aggregate(flows_23_typical[,4], list(as.character(flows_23_typical$time)), mean)
```

### Plot typical vs atypical
```{r}
flows_23_mean_combined <- data.frame("t"=flows_23_atypical_mean$Group.1, "flow_atypical"=flows_23_atypical_mean$flow, "flow_typical"=flows_23_typical_mean$flow)
# flows_23_mean_combined$t <- as.character(flows_23_mean_combined$t)
# flows_23_mean_combined$t <- chron::as.times(flows_23_mean_combined$t)
flows_23_mean_combined$t <- as.POSIXct(flows_23_mean_combined$t, format = "%H:%M:%S")
```

```{r}
flow_23_mean_compare <- ggplot(flows_23_mean_combined, aes(x = t)) +
  geom_line(aes(y = flow_atypical), colour = "red") +
  geom_line(aes(y = flow_typical), colour= "green") +
  scale_x_datetime(date_labels = "%H:%M") +
  theme_bw()
flow_23_mean_compare
```

## Cluster the flows based on ep-typical median value
```{r}
expected_flow_typ <- 
  flows_23_typical %>%
  mutate(time = hms::as_hms(t)) %>%
  #filter(!month(t) %in% c(3,4)) %>%
  group_by(o,d,time) %>%
  summarise(
    median_flow_typ = median(flow)
  )
```

```{r}
deviation_flow_typ <-
  flows_23_typical %>%
  mutate(time = hms::as_hms(t)) %>%
  group_by(o, d, time) %>%
  summarise(
    mad_flow_typ = mad(flow)
  )
```

```{r}
flow_with_expected <- inner_join(flow_with_expected, expected_flow_typ, by = c("o", "d", "time"))
```

```{r}
expected_flow_atyp <-
  flows_23_atypical %>%
  mutate(time = hms::as_hms(t)) %>%
  #filter(!month(t) %in% c(3,4)) %>%
  group_by(o,d,time) %>%
  summarise(
    median_flow_atyp = median(flow)
  )
```

```{r}
expected_flow_atyp_real <- 
  flows_23_atypical %>%
  filter(flow != 0) %>%
  group_by(o, d, time) %>%
  summarise(
    median_flow_atyp_real = median(flow)
  )
```


```{r}
deviation_flow_atyp <-
  flows_23_atypical %>%
  mutate(time = hms::as_hms(t)) %>%
  group_by(o, d, time) %>%
  summarise(
    mad_flow_atyp = mad(flow)
  )
```

```{r}
flow_with_expected <- inner_join(flow_with_expected, expected_flow_atyp, by = c("o", "d", "time"))
```

```{r}
flow_with_expected <- inner_join(flow_with_expected, expected_flow_atyp_real, by = c("o", "d", "time"))
```


```{r}
p_median_ep <- ggplot(flow_with_expected) + 
  geom_line(aes(x = time, y = flow, group = date(t)), color = "grey") +
  geom_line(aes(x = time, y = median_flow_typ), color = "black") +
  scale_x_time(
    name = "Time",
    breaks = hms::hms(hours = seq(2, 24, 4)),
    labels = scales::label_time("%H:%M")
  ) +
  theme_bw()
p_median_ep
```

```{r}
p_median_ep_atyp <- ggplot(flow_with_expected) + 
  geom_line(aes(x = time, y = flow, group = date(t)), color = "grey") +
  geom_line(aes(x = time, y = median_flow_atyp), color = "black") +
  scale_x_time(
    name = "Time",
    breaks = hms::hms(hours = seq(2, 24, 4)),
    labels = scales::label_time("%H:%M")
  ) +
  theme_bw()
p_median_ep
```

```{r}
p_median_comp <- 
  ggplot(flow_with_expected) +
  geom_line(
    aes(x = time, y = flow, group = date(t)),
    color = "grey"
  ) +
  geom_line(
    aes(x = time, y = median_flow, group = date(t)),
    linetype = "solid"
  ) +
  geom_line(
    aes(x = time, y = median_flow_typ, group = date(t)),
    linetype = "dotted"
  ) +
  geom_line(
    aes(x = time, y = median_flow_atyp, group = date(t)),
    linetype = "dashed"
  ) +
  theme_bw()
p_median_comp
```

```{r}
p_atypical_comp <- 
  ggplot(flow_with_expected) +
  geom_line(
    aes(
      x = time, 
      y = median_flow_atyp
      ),
    linetype = "solid"
  ) +
  geom_line(
    aes(
      x = time,
      y = median_flow_atyp_real
    ),
    linetype = "dashed"
  ) +
  theme(legend.position = "top") +
  xlab("Time") +
  ylab("Atypical Median") +
  theme_bw()
p_atypical_comp
```


```{r}
ggarrange(p_median, p_median_ep, 
          ncol = 3, nrow = 1)
```

### Variance comparison
```{r}
ggplot() +
  geom_line(
    data = deviation_flow,
    aes(x = time, y = mad_flow),
    linetype = "solid"
  ) +
  geom_line(
    data = deviation_flow_typ,
    aes(x = time, y = mad_flow_typ),
    linetype = "dotted"
  ) +
  geom_line(
    data = deviation_flow_atyp,
    aes(x = time, y = mad_flow_atyp),
    linetype = "dashed"
  ) +
  theme_bw()
```


## Flow-speed plot
```{r}
flows_23_typical %>% filter(month == 6) %>%
ggplot() +
  geom_point(aes(
    x = mean_speed, 
    y = flow
  )) + 
  theme_bw()
```

### Quadratic function fitting
```{r}
quad_fit <- lm(formula = flow ~ poly(mean_speed, 2, raw = TRUE), data = flows_23_weekday)
summary(quad_fit)
```

```{r}
quad_eq <- quad_fit$coefficient[3]*flows_23_weekday$mean_speed^2 + quad_fit$coefficient[2]*flows_23_weekday$mean_speed + quad_fit$coefficient[1]
quad_eq <- as.data.frame(quad_eq)
```

```{r}
quad_fit_plot <- flows_23_weekday %>%
  select(flow, mean_speed) %>%
  cbind(quad_eq)
quad_fit_plot
```


```{r}
p_quad_fit <-
  ggplot(quad_fit_plot) +
  # geom_point(
  #   aes(x = mean_speed, y = flow)
  # ) +
  geom_line(
    aes(x = mean_speed, y = quad_eq)
  )
p_quad_fit
```


```{r}
quad_fit_typical <- lm(formula = flow ~ poly(mean_speed, 2, raw = TRUE), data = flows_23_typical)
summary(quad_fit_typical)
```

```{r}
quad_fit_atypical <- lm(formula = flow ~ poly(mean_speed, 2, raw = TRUE), data = flows_23_atypical)
summary(quad_fit_atypical)
```

```{r}
# Pearson Correlation test entire for entire traffics
cor.test(flows_23_weekday$flow, flows_23_weekday$mean_speed, method = "pearson")

# Pearson Correlation test entire for typical traffics
cor.test(flows_23_typical$flow, flows_23_typical$mean_speed, method = "pearson")

# Pearson Correlation test entire for atypical traffics
cor.test(flows_23_atypical$flow, flows_23_atypical$mean_speed, method = "pearson")
```

```{r}
flows_23_2jan <-
  flow_with_expected %>%
  filter(as_date(t) == "2018-01-02") %>%
  mutate(quantile25 = quantile(flow, 0.25)) %>%
  mutate(start = hms::as_hms(t)) %>%
  mutate(end = hms::as_hms(start + hms::as_hms("00:15:00"))) %>%
  mutate(flow_diff = abs(flow - median_flow)) %>%
  mutate(condition = ifelse(flow_diff > quantile25, "ABNORMAL", "NORMAL"))
```


```{r}
p_clust_2jan <-
  ggplot(flows_23_2jan) +
  geom_line(
    aes(
      x = start,
      y = flow
      )
  ) +
  geom_rect(
    aes(
      xmin = start, 
      xmax = end, 
      fill = condition
      ),
    ymin = -Inf,
    ymax = Inf,
    alpha = 0.5
    ) +
  scale_fill_manual(values = c("grey", NA)) +
  xlab("Time") +
  ylab("Flow") +
  theme_bw()
p_clust_2jan
```

```{r}
sum(flows_23_2jan$condition == "ABNORMAL")/length(flows_23_2jan$condition)
```


```{r}
nrow(flows_23_weekday[flows_23_weekday$flow == 0,])/nrow(flows_23_weekday[flows_23_weekday$flow != 0,])*100
```

```{r}
expected_typical <- 
  flows_23_labelled %>%
  filter(cluster_label == "typical") %>%
  mutate(time = hms::as_hms(t)) %>%
  group_by(o, d, time) %>%
  summarise(
    median_typical = median(flow)
  )
```

```{r}
flow_with_expected <- inner_join(flow_with_expected, expected_typical, by = c("o", "d", "time"))
```

```{r}
flows_23_2jan_typ <-
  flow_with_expected %>%
  filter(as_date(t) == "2018-01-02") %>%
  mutate(quantile25 = quantile(flow, 0.25)) %>%
  mutate(start = hms::as_hms(t)) %>%
  mutate(end = hms::as_hms(start + hms::as_hms("00:15:00"))) %>%
  mutate(flow_diff = abs(flow - median_typical)) %>%
  mutate(condition = ifelse(flow_diff > quantile25, "ABNORMAL", "NORMAL"))
```

```{r}
p_clust_2jan_typ <-
  ggplot(flows_23_2jan_typ) +
  geom_line(
    aes(
      x = start,
      y = flow
      )
  ) +
  geom_rect(
    aes(
      xmin = start, 
      xmax = end, 
      fill = condition
      ),
    ymin = -Inf,
    ymax = Inf,
    alpha = 0.5
    ) +
  scale_fill_manual(values = c("grey", NA)) +
    xlab("Time") +
  ylab("Flow") +
  theme_bw()
p_clust_2jan_typ
```

```{r}
sum(flows_23_2jan_typ$condition == "ABNORMAL")/length(flows_23_2jan_typ$condition)
```

```{r}
flows_23_10jul <-
  flow_with_expected %>%
  filter(as_date(t) == "2018-07-10") %>%
  mutate(quantile25 = quantile(flow, 0.25)) %>%
  mutate(start = hms::as_hms(t)) %>%
  mutate(end = hms::as_hms(start + hms::as_hms("00:15:00"))) %>%
  mutate(flow_diff = abs(flow - median_flow)) %>%
  mutate(condition = ifelse(flow_diff > quantile25, "ABNORMAL", "NORMAL"))
```

```{r}
flows_23_10jul_typ <-
  flow_with_expected %>%
  filter(as_date(t) == "2018-07-10") %>%
  mutate(quantile25 = quantile(flow, 0.25)) %>%
  mutate(start = hms::as_hms(t)) %>%
  mutate(end = hms::as_hms(start + hms::as_hms("00:15:00"))) %>%
  mutate(flow_diff = abs(flow - median_typical)) %>%
  mutate(condition = ifelse(flow_diff > quantile25, "ABNORMAL", "NORMAL"))
```

```{r}
p_clust_10jul <-
  ggplot(flows_23_10jul) +
  geom_line(
    aes(
      x = start,
      y = flow
      )
  ) +
  geom_rect(
    aes(
      xmin = start, 
      xmax = end, 
      fill = condition
      ),
    ymin = -Inf,
    ymax = Inf,
    alpha = 0.5
    ) +
  scale_fill_manual(values = c("grey", NA)) +
    xlab("Time") +
  ylab("Flow") +
  theme_bw()
p_clust_10jul
```

```{r}
sum(flows_23_10jul$condition == "ABNORMAL")/length(flows_23_10jul$condition)
```


```{r}
p_clust_10jul_typ <-
  ggplot(flows_23_10jul_typ) +
  geom_line(
    aes(
      x = start,
      y = flow
      )
  ) +
  geom_rect(
    aes(
      xmin = start, 
      xmax = end, 
      fill = condition
      ),
    ymin = -Inf,
    ymax = Inf,
    alpha = 0.5
    ) +
  scale_fill_manual(values = c("grey", NA)) +
    xlab("Time") +
  ylab("Flow") +
  theme_bw()
p_clust_10jul_typ
```

```{r}
sum(flows_23_10jul_typ$condition == "ABNORMAL")/length(flows_23_10jul_typ$condition)
```

```{r}
fig1 <- ggarrange(p_clust_2jan, p_clust_2jan_typ,
          labels = c("A", "B"),
          ncol = 1, nrow = 2)

annotate_figure(fig1,
                top = text_grob("Abnormal flow detection on 2 January 2018", color = "Black", face = "bold", size = 12))
```

```{r}
fig2 <- ggarrange(p_clust_10jul, p_clust_10jul_typ,
          labels = c("A", "B"),
          ncol = 1, nrow = 2)

annotate_figure(fig2,
                top = text_grob("Abnormal flow detection on 10 July 2018", color = "Black", face = "bold", size = 12))
```

### Atypical Flow Analysis
```{r}
flows_23_atypical_real <-
  flows_23_atypical %>%
  filter(flow != 0) 
```

```{r}
flows_23_atypical_real %>%
filter(flow == 1)
```

```{r}
flows_23_atypical_real %>%
  filter(dayt == "2018-04-24")
```

